Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-03-23 AO_bondedSi.tex
incorporate DTJ edits up to page 21

where $\delta_{ij}$ is the Kronecker delta, and $\sigma_i$ are the independent measurement uncertainties on the $i^{\mathrm{th}}$ data point. We experimented with different values for $\sigma_i$.  When repeated DSP reference sample measurements were available, we estimated the $\sigma_i$ from the dispersion around mean-subtracted, detrended transmission spectra.  The parameter $s$ controls the correlation length, and $a$ controls the amplitude of the noise.  We do not know $a$ nor $s$ and they are, in general, different for each measurement.  The value of $a$ should be close to the mean drift reported in Table \ref{tabCary5000pars}.  The value of $s$ could be small (tens of nm) to capture local variation attributable to atmospheric air absorption, or large (hundreds or thousands of nm) to capture global features attributable to lamp drift.  We allow both $a$ and $s$ to be free parameters in our fitting procedure.

We set our prior probability distribution functions \cite{2013sdmm.book.....I}, $\ln{p(d,f,a,s)}$ as uniform over a wide range of values for $\ln{a}$, $\ln{s}$, $d$, and $f$ consistent with visual inspection of each spectrum.  The final un-normalized posterior probability function, expressed as a natural logarithm is:

@@

Figure \ref{figVG03full} shows a parameter determination for the measurement of a bond over a deep ($4000 \pm 200\;$nm) 100\% fill factor gap.  The analysis yields a best fit consistent with 100\% fill factor, and a depth of $3960 \pm 2\;$nm, well within the uncertainty of the physicsal measurement.  Figure \ref{figVG03part} shows a fit for a region of the same bonded pair where a nominally $4000\;$nm deep, 2 mm wide trench crosses the field scanned by the Cary 5000.  Analysis of this transmission curve gave a best fit depth of $4094 \pm 4\;$nm and a pattern fill factor of $4.6 \pm 0.1\;\%$, both consistent with the part geometry.  These two results show that the formalism performs as expected on resonant gaps several wavelengths deep.

@@

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG03_f100.pdf}
                \caption{Measured spectrum and fit of VG03 hole region}
                \label{figVG03_f100}
        \end{subfigure}
\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian Process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. VG03 has a gap of axial extent $\sim4\;\mu$m implanted in its interface.  The measured spectrum (black stepped line) in this region shows characteristic Fabry-P\`erot fringes of constructive and destructive interference.  The only tunable parameters of the model are the gap axial extent, $d$ and fill factor $f$.  No scaling has been applied.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model, described in the text.  Wavelengths shortward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.\label{figVG03full} }
\end{figure}

@@

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG03_f045.pdf}
                \caption{Measured spectrum and fit of VG03 petal region}
                \label{figVG03_f045}
        \end{subfigure}
\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where less than $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued Fabry-P\`erot fringes of constructive and destructive interference. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. \label{figVG03part}}
\end{figure}

\subsection{Spatially resolved measurements with Sample Transport Accessory}
We acquired spatially resolved measurements of sample VG09-12 with the Cary 5000 sample transport accessory \footnote{\url{http://www.chem.agilent.com/en-US/products-services/instruments-systems/molecular-spectroscopy/sample-transport-accessory/}}.  This accessory translates the sample through the measurement beam and takes a transmission spectrum at each position.  We chose a 2 mm step size, which is slightly larger than the $\sim1$ mm beam width.  We sampled 50 mm across the mesh pattern and into the off-mesh pattern (Figure \ref{figVG0912_STA_illus}).  The large number of consecutive measurements prevented the requisite near-contemporaneous baseline measurements for normalization.  We fit a line to before-and-after baseline measurements to infer the mean-level drift, which we divided out of each spectrum.  We reduced the measured wavelength range to $1250-1775\;$nm.

Figure \ref{figV09G12_STA_illus}) shows an illustration of sample VG09-12, with the approximate center locations of measurements marked with colored dots.  The colored dots match the color of the spectra in Figure \ref{figVG0912} The approximate size of the measurement beam is shown for scale.  The conspicuous mesh pattern has a lab measured depth of $49\pm6\;$nm, and global fill factor of 50\%.  However, since the beam size is comparable to mesh grid size, the achieved fill factor can vary from about 30\% to 75\%.  The gray band in Figure \ref{figVG0912} represents the allowable range of predictions, taking into account both the uncertainty in the mesh depth and fill factor.  If the mesh pattern were perfectly bonded, we would expect all the spectra to fall inside the color swath in Figure \ref{figVG0912}.  We see excellent consistency between prediction and measurement, though we cannot rule out the presence of extra gaps in the mesh area.  Outside the mesh area, the bonding is excellent, as demonstrated by the off-mesh transmission close to unity transmission.

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.35\textwidth}
              \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
              \caption{Illustration of VG09-12 sample transport accessory measurement positions}
		\label{figVG0912_STA_illus}
        \end{subfigure}
        \begin{subfigure}[b]{0.65\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
                \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh}
                \label{figVG0912}
        \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.
\label{figVG12}}
\end{figure}

>>>>

where $\delta_{ij}$ is the Kronecker delta, and $\sigma_i$ are the independent measurement uncertainties on the $i^{\mathrm{th}}$ data point. The parameter $s$ controls the correlation length, and $a$ controls the amplitude of the correlated noise.  We experimented with different values for $\sigma_i$.  When repeated double side polished reference sample measurements were available, we estimated the $\sigma_i$ from the dispersion around mean-subtracted, detrended transmission spectra.  We do not know $a$ nor $s$ and they are, in general, different for each measurement-- they are \emph{nuisance parameters}, and are ultimately marginalized out.  They arise from the uninteresting properties of the spectrometer, and their interpretation is immaterial.  The value of $a$ should be close to the mean drift reported in Table \ref{tabCary5000pars}.  The value of $s$ could be small (tens of nm) to capture local variation attributable to atmospheric air absorption, or large (hundreds or thousands of nm) to capture global features attributable to lamp drift.  We allow both $a$ and $s$ to be free parameters in our fitting procedure.

We set our prior probability distribution functions \cite{2013sdmm.book.....I}, $\ln{p(d,f,a,s)}$ as uniform over a wide range of values for $\ln{a}$, $\ln{s}$, $d$, and $f$, consistent with visual inspection of each spectrum.  The final un-normalized posterior probability function, expressed as a natural logarithm is:

@@

Figure \ref{figVG03full} shows a parameter determination for the measurement of a bond over a deep ($4000 \pm 200\;$nm) 100\% fill factor gap in part VG03.  The analysis yields a best fit consistent with 100\% fill factor, and a depth of $3960 \pm 2\;$nm, well within the uncertainty of the physical measurement (Table \ref{tbl_experiments}).  The spectrum in this region shows characteristic Fabry-P\`erot fringes of constructive and destructive interference.  The only tunable parameters of the model are the gap axial extent, $d$ and fill factor $f$.  No scaling has been applied to the curves in Figure \ref{figVG03full}.  Figure \ref{figVG03part} shows a fit for a region of the same bonded pair where a nominally $4000\;$nm deep, 2 mm wide trench crosses the field scanned by the Cary 5000.  Analysis of this transmission curve gave a best fit depth of $4094 \pm 4\;$nm and a pattern fill factor of $4.6 \pm 0.1\;\%$, both consistent with the part geometry.  These two results show that the formalism performs as expected on resonant gaps several wavelengths deep.

@@

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG03_f100.pdf}
                \caption{Measured spectrum and fit of VG03 hole region}
                \label{figVG03_f100}
        \end{subfigure}
\caption{ \emph{Top panel:} Corner plot of MCMC samples in our non-linear model fit of the transmission spectrum of Si optic part \# VG03.  The physical parameters of the model are the axial extent of the gap $d$, and the areal fill factor $f$ of the gap over the measurement region.  The MCMC model fit also includes nuisance parameters $a$ and $s$ (not shown) for the Gaussian process covariance model.  \emph{Bottom panel:}Transmission through bonded Si sample VG03, normalized by the transmission of a DSP Si wafer. See the text for details on the sample, setup, and analysis.  The measured spectrum is the black stepped line.  The red dashed line shows the best model fit with $d$ = 3960 $\pm$ 2 nm, consistent with 100\% fill factor.  The blue band shows the collective locations of 60 random draws from the Gaussian process model.  Wavelengths shortward of 1250 nm (gray band) were not included in the fit, since Si is absorptive there.\label{figVG03full} }
\end{figure}

@@

        \begin{subfigure}[b]{0.5\textwidth}
                \includegraphics[width=\textwidth]{figs/VG03_f045.pdf}
                \caption{Measured spectrum and fit of VG03 petal region}
                \label{figVG03_f045}
        \end{subfigure}
\caption{ Same as Figure \ref{figVG03full}, but the measurement was in a region where $<5\%$ of the area exhibited the $\sim4\; \mu$m gap.  The measured spectrum in this region shows subdued fringes. The model derived axial extent is 4094 $\pm$ 5 nm covering a fill factor of 4.58 $\pm$ 0.06$\%$. \label{figVG03part}}
\end{figure}

\subsection{Spatially resolved measurements with Sample Transport Accessory}
We acquired spatially resolved measurements of the pair of bonded parts VG09-12, (Tables \ref{tbl_experiments} and \ref{tbl_meshPatterns}) with the Cary 5000 sample transport accessory \footnote{\url{http://www.chem.agilent.com/en-US/products-services/instruments-systems/molecular-spectroscopy/sample-transport-accessory/}}.  This accessory translates the sample through the measurement beam and takes a transmission spectrum at each position.  We chose a 2 mm step size, which is slightly larger than the $\sim1$ mm beam width.  We sampled 50 mm across the mesh pattern and into the off-mesh pattern (Figure \ref{figVG0912_STA_illus}).  The large number of consecutive measurements prevented the requisite near-contemporaneous baseline measurements for normalization.  We fit a line to before-and-after baseline measurements to infer the mean-level drift, which we divided out of each spectrum.  We measured over a wavelength range from 1250 to 1775 nm.

Figure \ref{figV09G12_STA_illus} shows an illustration of sample VG09-12, with the approximate center locations of measurements marked with colored dots.  The colored dots match the color of the spectra in Figure \ref{figVG0912} The approximate size of the measurement beam is shown for scale.  The conspicuous mesh pattern has a lab measured depth of $49\pm6\;$nm, and global fill factor of 50\%.  However, since the beam size is comparable to mesh grid size, the achieved fill factor can vary from about 30\% to 75\%.  The gray band in Figure \ref{figVG0912} represents the allowable range of predictions, taking into account both the uncertainty in the mesh depth and fill factor.  If the mesh pattern were perfectly bonded, we would expect all the spectra to fall inside the color swath in Figure \ref{figVG0912}.  We see excellent consistency between prediction and measurement, though we cannot rule out the presence of extra gaps in the mesh area.  Outside the mesh area, the bonding is excellent, as demonstrated by the off-mesh transmission close to unity transmission.

\begin{figure}[htbp]
        \centering
        \begin{subfigure}[b]{0.35\textwidth}
              \includegraphics[width=\textwidth]{figs/VG09_12_STA_illustration.pdf}
              \caption{Illustration of VG09-12 sample transport accessory measurement positions \label{figVG0912_STA_illus}}
        \end{subfigure}
        \begin{subfigure}[b]{0.65\textwidth}
                \includegraphics[width=\textwidth]{figs/VG0912_STA_scan_coarse.pdf}
                \caption{Measured gap transmission spectra of VG09-12 on- and off- mesh \label{figVG0912}}
        \end{subfigure}
\caption{Predictions and measurements of the coarse mesh region in sample VG09-12.  We took 50 measurements across the face of VG09-12, including both on- and off- mesh regions.  The measurements are consistent with the predicted transmission, shown as the gray band.  The off-mesh regions demonstrate near-perfect bonding.
\label{figVG12}}
\end{figure}
